---
title: "A4Q2"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Undergraduate Student

## (i)

```{r}
library(leaps)
set.seed(6)
college <- read.csv("College.csv", header=T)[,-c(1)]
college$Private <- as.numeric(as.factor(college$Private))
s <- sample(nrow(college), nrow(college)*0.7)
train <- college[s,]
test <- college[-s,]
step <-regsubsets(Outstate~., data=train, method="forward", nvmax=ncol(train)-1)
subsummary <- summary(step)
plot(subsummary$cp,type="o",col="red",main="cp",ylab="cp")
abline(h=min(subsummary$cp),col="blue")
plot(subsummary$bic,type="o",col="red",main="bic",ylab="bic")
abline(h=min(subsummary$bic),col="blue")
plot(subsummary$adjr2,type="o",col="red",main="adjr2", ylab="adjr2")
abline(h=max(subsummary$adjr2),col="blue")
plot((subsummary$rss/nrow(train)),type="o",col="red",main="rmse", ,ylab="rmse")
abline(h=min(subsummary$rss/nrow(train)),col="blue")

which.min(subsummary$cp)
which.min(subsummary$bic)
which.max(subsummary$adjr2)
which.min(subsummary$rss/nrow(train))
```

6 is the best minimum size we can get from four graphs. 


```{r}
subsummary
```


We get Private, Room.Board, Expend, Grad.Rate, perc.alumni, Terminal


## (ii)

```{r}
library(gam)
gamfit <- gam(Outstate~Private+s(Room.Board)+s(Expend)+s(Grad.Rate)+
                s(perc.alumni)+s(Terminal),data = train)
par(mfrow=c(2,3))
plot(gamfit, se=T)
```

**Comments:** From graphs, we see that there might exist non-linear relationship between OutState and Room.Board, OutState and Expend.


## (iii)

```{r}
pred <- predict(gamfit, test)
mse <- mean((test$Outstate-pred)^2)
tss <- mean((test$Outstate-mean(test$Outstate))^2)
R <- 1 - mse/tss
mse
R
```

**Comments:** After applying the model to test data set, we get mean square error 3627254 and R squared 0.7667036. This shows that this model does not perform extremely well.


## (iv)

```{r}
summary(gamfit)
```

**Comments:** From Anova Test for Nonparametric Effects, we see that the p-value of Expend is extremely small and Room.Board is smaller than 0.05. This means that there is a really strong evidence that Expend has a non-linear relationship with OutState, and there is an evidence that Room.Board might have non-linear relationship with OutState. This matches our conclusion in part ii.

