---
title: "A2Q3"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Undergraduate Student**

```{r}
enzyme <- read.delim("Enzyme.txt")
```


## (i)

```{r}
enzyme <- read.delim("Enzyme.txt")
enzyme$Y <- 1/enzyme$Y
enzyme$x <- 1/enzyme$x
init <- lm(Y~x, data = enzyme)
summary(init)

# beta 0
alpha0 <- summary(init)$coefficient[1,1]
beta0 <- 1/alpha0
beta0

# beta 1
alpha1 <- summary(init)$coefficient[2,1]
beta1 <- alpha1*beta0
beta1
```


## (ii)

```{r}
enzyme <- read.delim("Enzyme.txt")
library(MASS)
par.ini = c(b0 = beta0, b1 = beta1)
nonlinear <- nls(Y~(b0*x)/(b1+x), data = enzyme, start = par.ini, trace = TRUE)
summary(nonlinear)

# beta 0 
beta0 <- summary(nonlinear)$coefficient[1,1]
beta0

# beta 1
beta1 <- summary(nonlinear)$coefficient[2,1]
beta1
```


## (iii)

```{r}
plot(enzyme$x, enzyme$Y, xlab = "x", ylab = "Y", main = "Y vs x")
xx <- enzyme$x
yy <- (beta0*xx)/(beta1+xx)
points(xx, yy, "l", col = "red")
```

**Comments:** We see that the line matches the pattern of the data points. The model fit appears to be adequate.


## (iv)

```{r}
plot(fitted.values(nonlinear), residuals(nonlinear), xlab = "fitted values", 
     ylab = "residuals", main = "residuals vs fitted values")
abline(h=0, col = 'red')

plot(enzyme$x, residuals(nonlinear), xlab = "x", ylab = "residuals",
     main = "residuals vs x")
abline(h=0, col = 'red')

library(car)
qqPlot(residuals(nonlinear))
```

**Comments:** Three graphs show that residuals are well-behaved and follow normality condition. Except for point 3 and point 11, these two points potentially can be outliers.


## (v)

If we use fewer points with replications, since the some of data points have the same Y, the model can fit the data better when minimizing residuals. Therefore, the fitted line can be closer to all data points and reduce bias. On the other hand, since the fitted model has low bias, the model will have high variance. This means that the model does not generalized on the original data, or perform badly on original data. Also, since data are replicated, the residuals are not following normality conditions anymore. We can see a clear pattern on residual plot.


## (vi)

### (a)

```{r}
confint(nonlinear, "b0", level=0.95)
```

The confidence interval is (26.64509, 29.79721).


### (b)

$H_0=20$ vs $H_A \neq 20$:

```{r}
tstat <- (beta1 - 20)/(summary(nonlinear)$coefficient[2,2]/sqrt(18))
tstat

pval <- 2*pt(tstat, df=18-1)
pval
```

**Comment:** Since the t-statistics is way smaller than the critical value 0.05, there is a strong evidence against the null hypothesis and we reject the null hypothesis. We conclude that beta 1 can not be 20.
