---
title: "A1Q8"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Undergraduate Student**

```{r}
overdue <- read.csv("overdue.txt",sep = "\t")
type <- c(rep(0, 48), rep(1,48))
overdue$TYPE <- type
summary(lm(LATE~BILL+TYPE, data = overdue))
```

We found that BILL predictor has a p-value greater than 0.05, this indicates that it is not significant. We should preceed to reduced models.

**Reduced model:**

```{r}
summary(lm(LATE~BILL, data = overdue))
summary(lm(LATE~TYPE, data = overdue))
```

We see that reduced models do not improve the model results. We have to check we can add some interaction terms.

**Full interaction model:**

```{r}
summary(lm(LATE~BILL*TYPE, data = overdue))
```

First we tried full interaction model. p-values of all predictors including interaction term are significant. However, the p-value of the intercept indicates that this is not a appropriate model even it has a really high R-squared value.

We have to try one predictors and one interaction term.

**One predictor with one interaction:**

```{r}
summary(lm(LATE~BILL+BILL:TYPE, data = overdue))
summary(lm(LATE~TYPE+BILL:TYPE, data = overdue))
```

For these two models, we can see that the second model is better than the first one because it has good R-squared value (0.8313), and all predictors including intercept have really small p-value. This means that the model can not be further optimized. 


**Therefore, we will use LATE~TYPE+TYPE:BILL as our regression model**